Developing Data Products-Week 3 Assignment
========================================================
author: Ayah Fouad
date: May 28th 2019
autosize: true

Introduction
========================================================



- This project was created as part of the Developing Data Products course of the Coursera Data Science Specialisation.

- The goal of the project is to create a web page presentation using R Markdown that features a plot created with Plotly, and to host the resulting web page on either GitHub Pages, RPubs, or NeoCities.

- The interactive plot on the next slide represents the number of road accidents in Great Britain from 2005 to 2015, grouped by severity (slight, serious, or fatal).

R Code
========================================================
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=TRUE, cache=TRUE}
library(plotly)

```

Plot Result
========================================================

```{r, echo=FALSE}
plot_ly(data = mtcars, x = ~wt, y = ~mpg, 
        color = ~as.factor(cyl), size = ~hp,
        text = ~paste("Weight: ", wt, '<br>MPG:', mpg),
        type = "scatter", mode = "markers") %>%
  layout(title = "Car Data")
```
